MLH1 data report 

### 2017-10-22 rmd_report.rmd
still working on pvalue comparison

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(ggplot2)
library(pwr)
library(plyr)
library(lattice)
library(dplyr)
#setwd("C:/Users/alpeterson7/Documents/MLH1repo")
load(file="MLH1_data_setup.RData")

@@

colnms = c("mouse", "rep")

#makes dfs, with the samples 
permut.mouse.numb <- function(x, rep_size, samp_size){
  new.df = matrix(nrow=rep_size, ncol=samp_size)
for(i in 1:rep_size) {
  new.df[i,] = sample(x, samp_size)
  }
return(as.data.frame(new.df, colnames(colnms) ) )
}

ply_data <- df.pasd.mice[df.pasd.mice$mouse == "8oct14_PWD_f8",]
#make this the function that I apply over the mice in the data

@@

#repeat the sampling 100 times

bb <-ddply(jj, .(mouse), function(x) t.test(x[1,2:5],x[2,2:5])$p.value )#t.test for 2

@@

hundred <- function(x){
  plist=data.frame(pv=as.numeric(), mean1=as.numeric(), mean2=as.numeric())
  for(eye in 1:100){
    samp1 = sample(x, 5)
    samp2 = sample(x, 5)
    plist$pv[eye] <- t.test(samp1,samp2)$p.value
    plist$mean1[eye] <- mean(samp1)
    plist$mean2[eye] <- mean(samp2)
  }
  return(plist)
}

mm <- hundred(ply_data$nMLH1.foci)

#this works
vv <-permut.mouse.numb(df.pasd.mice$nMLH1.foci,5,2)

##
## I think this does it! this makes a list of 23 dfs (for each mouse in the large df)
kk<-dlply(df.pasd.mice, .(mouse), function(x) permut.mouse.numb(x$nMLH1.foci,2,5) )

jj<-ddply(df.pasd.mice, .(mouse), function(x) permut.mouse.numb(x$nMLH1.foci,2,10) )

#t.test and p values
#maybe I should just choose 2 samples, do a t.test, do that 100 times..?
#below runs t.tests on 
bb <-ddply(jj, .(mouse), function(x) t.test(x[1,2:5],x[2,2:5])$p.value )#t.test for 2 samples of size 10

@@

# this creates dataframe, which is a subset of larger dataframe ... not sure se_alone, but samples 40 of 
this =ddply (df.pasd.mice, .(mouse), subset, sample(seq_along(nMLH1.foci)<=5))

ss <- sample(df.pasd.mice$nMLH1.foci)

>>>>

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(ggplot2)
library(pwr)
library(plyr)
library(lattice)
library(dplyr)
#setwd("C:/Users/alpeterson7/Documents/MLH1repo")
load(file="MLH1_data_setup.RData")
```

@@

colnms = c("mouse", "rep")
ply_data <- df.pasd.mice[df.pasd.mice$mouse == "8oct14_PWD_f8",]
#make this the function that I apply over the mice in the data

@@

#repeat the sampling 100 times
bb <-ddply(jj, .(mouse), function(x) t.test(x[1,2:5],x[2,2:5])$p.value )#t.test for 2

@@

hundred <- function(x){
  plist=data.frame(pv=as.numeric(), mean1=as.numeric(), mean2=as.numeric())
  for(eye in 1:100){
    samp1 = sample(x, 5)
    samp2 = sample(x, 5)
    plist$pv[eye] <- t.test(samp1,samp2)$p.value
    plist$mean1[eye] <- mean(samp1)
    plist$mean2[eye] <- mean(samp2)
  }
  return(plist)
} 
mm <- hundred(ply_data$nMLH1.foci)

#makes dfs, with the samples. // sampling from MLH1
permut.mouse.numb <- function(x, rep_size, samp_size){
  new.df = matrix(nrow=rep_size, ncol=samp_size)
for(i in 1:rep_size) {
  new.df[i,] = sample(x, samp_size)
  }
return(as.data.frame(new.df, colnames(colnms) ) )
  #return sampled
}
#can I integrate the sampling and t.test here?

#function for

#this works. sampling x permutations, y sample size
vv <- permut.mouse.numb(df.pasd.mice$nMLH1.foci,5,4)

## I think this does it! this makes a list of 23 dfs (for each mouse in the large df)
##this makes dfs for doing the t.tests
kk<-dlply(df.pasd.mice, .(mouse), function(x) permut.mouse.numb(x$nMLH1.foci,2,5) )
#applies permut function over mouse -- then run a t.test and return pvalue
jj<-ddply(df.pasd.mice, .(mouse), function(x) permut.mouse.numb(x$nMLH1.foci,2,20) )

#
pval <- function()

#t.test and p values
#maybe I should just choose 2 samples, do a t.test, do that 100 times..?
#below runs t.tests on
#this is making a new tab;e, 
bb <- ddply(jj, .(mouse), function(x) t.test(x[1,2:5],x[2,2:5])$p.value )#t.test for 2 samples of size 20

# figure out a way to mush dd into a matrix

repeats = 10
new.p.matrix = matrix(ncol=length(unique(jj$mouse)), nrow = repeats)
for(e in 1:repeats){
  new.p.matrix[e]<- ddply(jj, .(mouse), function(x) t.test(x[1,2:5],x[2,2:5])$p.value )

  }

powrange <- seq(0.4, .9, .1)
n <- sapply(powrange, function(i) power.prop.test(p1=0.4,p2=0.24,power=i,sig.level=0.05)$n)
plot(powrange, n)

bb$mouse[(bb$V1 < 0.05)]
#mice which had significantly difference in samples of size 20
#16jan16_G_f2  20feb16_G_f3  3nov15_WSB_f1
#17mar16_G_f1
#16jan16_G_f2   20dec16_LEW_m3
#30sep16_MSM_f2
#22jun15_G_m2

#figure out how to permute these tests. repeat the above... then return distributions of p values

#10
#20feb16_G_f3   13nov16_MSM_m1

@@

# this creates dataframe, which is a subset of larger dataframe ... not sure se_alone, but samples 40 of 
this =ddply (df.pasd.mice, .(mouse), subset, sample(seq_along(nMLH1.foci)<=5))
#ss <- sample(df.pasd.mice$nMLH1.foci)
